Grove: A Convergent Collaborative Structure-Editor Calculus

### 2020-09-23 grove-paper.tex
Add vertexes, constructors, and positions to section 3.2.1 graph formalism (Eric)

% sets
\def\A{\mathcal{A}}
\def\C{\mathcal{C}}
\def\E{\mathcal{E}}
\def\G{\mathcal{G}}
\def\I{\mathcal{I}}
\def\K{\mathcal{K}}
\def\S{\mathcal{S}}
\def\U{\mathcal{U}}
\def\V{\mathcal{V}}
\def\e{\varepsilon}
\def\AA{\textbf{A}}
\def\EE{\textbf{E}}

@@

A graph $\G : \E \rightarrow \Sigma$ is a function from edges to edge states, 
where $\E = \U \times \V \times \I \times \V$ 
and   unique IDs are drawn from some suitable set $\U$
and   vertices are drawn from $\V$, 
and   indices are drawn from $\I$, 
and   edge states are drawn from $\Sigma$, all defined below.

Each edge, $\e = (u, v_s, p, v_t)$, has a unique name, $u \in \U$, and connects the child position $p$ of a source vertex $v_s$ to a target vertex $v_t$.
The state of each edge, $\e$, is determined by the corresponding edge state, $\G(\e) \in \Sigma = \{ \bot, \Plus, \Minus \}$. 
If $\G(\e) = \bot$, then $\e$ does not yet exist.
If $\G(\e)$ is $\Plus$, the edge has been created.
If $\G(\e)$ is $\Minus$, the edge has been destroyed.
The total ordering $\bot \sqsubset \Plus \sqsubset \Minus$ forms a lattice over $\Sigma$.

A vertex $v = (u, k) \in \U \times \K$ is a pair of a globally unique identifier $u$ and a constructor $k$. We say $u$ identifies vertex $v$ as a distinct instance of constructor $k$.

Define $\sqcup_{edge state}$ (i.e. join)

lattice ordering $\bot < + < -$ LUB e.g., join A B = C

@@

\begin{tabular}{cl@{\hspace{1.5cm}}cl@{\hspace{1.5cm}}cl@{\hspace{1.5cm}}cl}
  $\A$ & Actions & $\S$ & Edge States   \\
  $\C$ & Cursors & $\U$ & UUIDs         \\
  $\E$ & Edges   & $\V$ & Vertexes      \\
  $\G$ & Graphs  & $\A$ & Graph Actions \\
  $\I$ & Indices & $\E$ & Editors       \\
  $\K$ & Constructors                   \\
\end{tabular}

>>>>

% sets
\def\A{\mathcal{A}}
\def\C{\mathcal{C}}
\def\E{\mathcal{E}}
\def\G{\mathcal{G}}
\def\I{\mathcal{I}}
\def\K{\mathcal{K}}
\def\P{\mathcal{P}}
\def\S{\mathcal{S}}
\def\U{\mathcal{U}}
\def\V{\mathcal{V}}
\def\e{\varepsilon}
\def\AA{\textbf{A}}
\def\EE{\textbf{E}}

@@

A graph $\G : \E \rightarrow \Sigma$ is a function from edges to edge states, 
where $\E = \U \times \V \times \P \times \V$,
and   unique IDs are drawn from some suitable set $\U$,
and   vertices are drawn from $\V$, 
and   positions are drawn from $\P$, 
and   edge states are drawn from $\Sigma$, all defined below.

Each edge $\e = (u, v, p, v^\prime)$ has a unique name, $u \in \U$, and connects the child position $p$ of a source vertex $v$ to a target vertex $v^\prime$.
The state of each edge, $\e$, is determined by the corresponding edge state, $\G(\e) \in \Sigma = \{ \bot, \Plus, \Minus \}$.
If $\G(\e) = \bot$, then $\e$ does not yet exist.
If $\G(\e)$ is $\Plus$, the edge has been created.
If $\G(\e)$ is $\Minus$, the edge has been destroyed.
The total ordering $\bot \sqsubset \Plus \sqsubset \Minus$ forms a lattice over $\Sigma$.

A vertex $v = (u, k)$ identifies a distinct instance of the constructor $k$.
Each constructor represents a different type of node in the target language's abstract syntax tree.

A position $p$ identifies a location adjacent to some parent vertex.

Every graph contains a distinguished root vertex, root constructor, and root position, respectively named $v_0$, $k_0$, and $p_0$.

% Define $\sqcup_{edge state}$ (i.e. join)

% lattice ordering $\bot < + < -$ LUB e.g., join A B = C

@@

\begin{tabular}{cl@{\hspace{1.5cm}}cl@{\hspace{1.5cm}}cl@{\hspace{1.5cm}}cl}
  $\A$ & Actions & $\S$ & Edge States   \\
  $\C$ & Cursors & $\U$ & UUIDs         \\
  $\E$ & Edges   & $\V$ & Vertexes      \\
  $\G$ & Graphs  & $\AA$ & Graph Actions \\
  $\I$ & Indices & $\EE$ & Editors       \\
  $\K$ & Constructors                   \\
\end{tabular}
